---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MD-ALL 
#### Molecular Diagnosis of Acute Lymphoblastic Leukemia

## Installation
You can install the released version of MD-ALL from [github](https://github.com/gu-lab20/MD-ALL).

| Type        | Command                                             |
|-------------|-----------------------------------------------------|
| Development | `devtools::install_github("gu-lab20/MD-ALL")`       |


## Load required library
```{r loading packages,message=FALSE,warning=FALSE,error=FALSE}
library(MDALL)
library(dplyr)
library(Rtsne)
library(ggplot2)
library(ggrepel)
library(umap)
library(Rphenograph)
library(SummarizedExperiment)
```

## Import data
The count data can be imported directory from a txt file, separated by space, tab or common. 
The HTSeqCount generated gene level count are accepted for now. Later we will add the support for featureCounts.
The ENSG id should be used as the gene name.

```{r}
df_count=read_input("tests/test.HTSeqCount",delimiter = "\t",header = F)
dim(df_count)
head(df_count)
tail(df_count)
```

## Normalization
Normalization with reference data

```{r,message=FALSE,warning=FALSE,error=FALSE}
df_vst=get_vst_values(obj_in = obj_234_HTSeq,df_count = df_count)
dim(df_vst)
head(df_vst)
tail(df_vst)
```

## Add testing sample to reference dataset for subtype prediction
```{r,message=FALSE,warning=FALSE,error=FALSE}
obj_=obj_merge(obj_in = obj_2042_HTSeq,df_in = df_vst,assay_name_in = "vst")
```

## Run tSNE
```{r,message=FALSE,warning=FALSE,error=FALSE}
obj_=run_tsne(obj_in = obj_,out_label = "tsne",feature_panel = "boruta_genes")
```

## Draw tSNE plot
```{r,fig.width=9,fig.height=8}
p1=draw_DimPlot(obj_,group.by = "diag",reduction = "tsne",highlightLevel = "TestSample")
p1
```

##Run uMAP
```{r,message=FALSE,warning=FALSE,error=FALSE}
obj_=run_umap(obj_in = obj_,out_label = "umap",n_neighbors = 30,variable_n = 800,feature_panel = "boruta_genes")
```

## Draw uMAP plot
```{r,fig.width=9,fig.height=8}
p2=draw_DimPlot(obj_,group.by = "diag",reduction = "umap",highlightLevel = "TestSample")
p2
```

## Run PhenoGraph Clustering
```{r,message=FALSE,warning=FALSE,error=FALSE}
obj_=run_PhenoGraph(obj_in = obj_,feature_panel = "boruta_genes",variable_n = 800,neighbor_k = 30)
```
```{r}
get_PhenoGraphPred(obj_)
```

## Load ShinyApp
```{r}

```


































