---
title: "MD-ALL Introduction"
author: "Zunsong Hu"
date: "11/8/2022"
package: MDALL
output: html_document
vignette: >
  %\VignetteIndexEntry{An introduction to the MD-ALL}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<strong>MD-ALL</strong> is an R package used to do ALL subtyping based on bulk-RNAseq data.

## Install

```{r}
library(MDALL)
library(dplyr)
library(Rtsne)
library(ggplot2)
library(ggrepel)
library(SummarizedExperiment)
```

## Import data
The count data can be imported directory from a txt file, separated by space, tab or common. 
Both HTSeqCount and featureCounts generated gene level count are accepted.
The ENSG id should be used as the gene name.

```{r}
df_count=read_input("../tests/test.HTSeqCount",delimiter = "\t",header = F)
dim(df_count)
head(df_count)
tail(df_count)
```
## Normalization
Normalization with reference data

```{r}
df_vst=get_vst_values(file_obj="../data-raw/obj_234_HTSeqCountMini.rds",df_count = df_count)
dim(df_vst)
head(df_vst)
tail(df_vst)
```
## Add testing sample to reference dataset for subtype prediction
```{r}
obj_out=obj_merge(file_obj = "../data-raw/obj_2042_HTSeqCountMini.rds",df_in = df_vst,assay_name_in = "vst")
```

## Run tsne
```{r}
obj_out=run_tsne(obj_in = obj_out,out_label = "tsne",feature_panel = "boruta_genes")
```
```{r}
cols_in=subtypeCol()[names(subtypeCol()) %in% obj_out$SE$diag ]
table(obj_out$SE$diag)
p1=draw_DimPlot(obj_out,group.by = "diag",cols = cols_in,reduction = "tsne")  
p1

```

```{r}
df_tsne=get_embeding_feature(obj_in=obj_out,features="diag")

df_testSample=df_tsne[df_tsne$diag=="TestSample",]

p1+geom_point(data=df_testSample, aes(tSNE_1, tSNE_2, color=diag), size=2)+
    geom_text_repel(data=df_testSample, aes(tSNE_1, tSNE_2, label=diag), fontface = "bold")

```



```{r pressure, echo=FALSE}
plot(pressure)
```


